Timid tides or tall tails? \\ Investigating the outer reaches of the Sculptor and Ursa Minor dwarf galaxies

### 2025-04-24 thesis/introduction.tex
tests to validate gaia filters and thesis updates

\begin{table*}[t]
\centering
\caption{Observed properties of Ursa Minor. References are: (1) Muñoz et al. (2018), (2) Garofalo et al. (2025), (3) McConnachie and Venn (2020), (4) average of Pace et al. (2020) and Spencer et al. (2018).}
\label{tbl:Observed-properties-of-Ursa-Minor-References-are:-1-Muñoz-et-al-2018-2-Garofalo-et-al-2025-3-McConnachie-and-Venn-2020-4-average-of-Pace-et-al-2020-and-Spencer-et-al-2018}
\begin{tabular}{lll}
\toprule
parameter & value & Source\\
\midrule
$\alpha$ & $ 227.2420 \pm 0.0045$˚ & 1\\
$\delta$ & $67.2221 \pm 0.0016$˚ & 1\\
distance modulus & $19.23 \pm 0.11$ (RRL) & 2\\
distance & $70.1 \pm 3.6$ kpc & -\\
$\mu_\alpha*$ & $-0.124 \pm 0.004 \pm 0.017$ mas yr$^{-1}$ & 3\\
$\mu_\delta$ & $0.078 \pm 0.004_{\rm stat} \pm 0.017_{\rm sys}$ mas yr$^{-1}$ & 3\\
radial velocity & $-245.8 \pm 0.3_{\rm stat} \pm 1_{\rm sys}$ km s$^{-1}$ & this work\\
$\sigma_v$ & $8.8 \pm 0.2$ & this work\\
$r_h$ & $18.2 \pm 0.1$ arcmin & 1\\
ellipticity & $0.55 \pm 0.01$ & 1\\
position angle & $50 \pm 1^\circ$ & 1\\
$M_V$ & $-9.03 \pm 0.05$ & 1\\
\bottomrule
\end{tabular}
\end{table*}

@@

\section{What is up with
probabilities}\label{what-is-up-with-probabilities}

\begin{figure}
\centering
\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{/Users/daniel/Library/Application Support/typora-user-images/image-20250416112038183.png}
\caption{image-20250416112038183}\label{fig:test}
\end{figure}

>>>>

\begin{table*}[t]
\centering
\caption{Observed properties of Ursa Minor. References are: (1) Muñoz et al. (2018), (2) Garofalo et al. (2025), (3) McConnachie and Venn (2020), (4) average of Pace et al. (2020) and Spencer et al. (2018).}
\label{tbl:Observed-properties-of-Ursa-Minor-References-are:-1-Muñoz-et-al-2018-2-Garofalo-et-al-2025-3-McConnachie-and-Venn-2020-4-average-of-Pace-et-al-2020-and-Spencer-et-al-2018}
\begin{tabular}{lll}
\toprule
parameter & value & Source\\
\midrule
$\alpha$ & $ 227.2420 \pm 0.0045$˚ & 1\\
$\delta$ & $67.2221 \pm 0.0016$˚ & 1\\
distance modulus & $19.23 \pm 0.11$ (RRL) & 2\\
distance & $70.1 \pm 3.6$ kpc & -\\
$\mu_\alpha*$ & $-0.124 \pm 0.004 \pm 0.017$ mas yr$^{-1}$ & 3\\
$\mu_\delta$ & $0.078 \pm 0.004_{\rm stat} \pm 0.017_{\rm sys}$ mas yr$^{-1}$ & 3\\
radial velocity & $-245.9 \pm 0.3_{\rm stat} \pm 1_{\rm sys}$ km s$^{-1}$ & this work\\
$\sigma_v$ & $8.8 \pm 0.2$ & this work\\
$r_h$ & $18.2 \pm 0.1$ arcmin & 1\\
ellipticity & $0.55 \pm 0.01$ & 1\\
position angle & $50 \pm 1^\circ$ & 1\\
$M_V$ & $-9.03 \pm 0.05$ & 1\\
\bottomrule
\end{tabular}
\end{table*}

@@
